Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
Five of us evaluated the papers

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
scoring_criteria %>%
  rename(`Index Value` = Index.Value) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_table_properties(layout = "autofit") %>%
  set_caption(
    "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by four independent assessors to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
```

>>>>

```{r scoring, echo=FALSE, message=FALSE, warning=FALSE}
scoring_criteria %>%
  rename(`Index Value` = Index.Value) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_table_properties(layout = "autofit") %>%
  set_caption(
    "Articles were scored in four areas for reproducibility on a scale of '0' to '3' by five independent evaluators to rank articles in each of four areas, 'Computational methods availability', 'Data availability', 'Software availability' and 'Software citation'.")
```
